---
title: "Akram_LandGeoLot_EDA"
output: html_document
---

Load packages:

```{r}
library(Quandl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(tidyquant)
library(patchwork)
library(lubridate)
library(zoo)
library(Hmisc)
library(ggcorrplot)
library(corrplot)
library(ggpubr)

path = "~/Desktop/NYCDSA/Homework/Project3/Akram/1 - EDA"
setwd(path)

```

Import data frames:

```{r}

df_cleaned = read.csv("~/Desktop/NYCDSA/Homework/Project3/Akram/Data/cleaned.csv")

df_engineered = read.csv("~/Desktop/NYCDSA/Homework/Project3/Akram/Data/engineered.csv")

Ames_Start = as.Date("2006-01-01")
Ames_End = as.Date("2010-12-31")

TNX = tq_get("^TNX",
             from = Ames_Start,
             to = Ames_End,
             get = "stock.prices"
             ) %>%
  select(date, adjusted) %>%
  rename(rate = adjusted)

TNX = TNX %>%
  group_by(DateSold = lubridate::floor_date(date, "month")) %>%
  summarise(Rate = mean(rate, na.rm=TRUE))

head(TNX)

df_cleaned = df_cleaned %>% 
  mutate(
    DaySold = as.integer(1), 
    DateSold = make_date(YrSold,MoSold,DaySold)
  )

df_cleaned = df_cleaned %>%
  relocate(DateSold, .after = PID) %>%
  relocate(SalePrice, .before = GrLivArea) %>%
  select(-c(X, YrSold, MoSold, DaySold)) %>%
  arrange(ymd(df_cleaned$DateSold), SalePrice)

head(df_cleaned)

```

Merge interest rate with main dataframe:

```{r}

# First, create logSalePrice column

df_cleaned$logSalePrice = log10(df_cleaned$SalePrice)

# Merge TNX with df_cleaned

df_cleaned = df_cleaned %>%
  left_join(TNX, by="DateSold") %>%
  relocate(Rate, .after = SalePrice) %>%
  relocate(logSalePrice, .after = SalePrice)

head(df_cleaned)

```


Feature extraction for Land/Geography/Lot section:

LotFrontage (feet): Linear feet of street connected to property (lots of NaN's - filled in with sqrt(LotArea) - could do with regression with LotArea). In my opinion, this category should be deleted.

LotArea (feet^2): Lot size in square feet

YearBuilt (YYYY): Original construction date
YearRemodAdd (YYYY): Remodel date (same as construction date if no remodeling or additions)
We will replace these categories with:
Age - year(DateSold) minus YearBuilt
YrsSinceRemod - year(DateSold) minus YearRemodAdd

Street (Grvl / Pave): Type of road access to property
Alley (NoAlley / Grvl / Pave): Type of alley access to property
N.B. There are no entries where: 1) Street = Grvl & Alley = Grvl
2) Street = Grvl & Alley = Pave
So there is only: 0) Grvl/NoAlley 1) Pave/NoAlley 2) Pave/Grvl 3) Pave/Pave
This is how we'll categorise the data in a new joint category: 
StreetAlley - 0, 1, 2, 3

```{r}
#df_1 = filter(df_cleaned, Street == "Pave" & Alley == "Pave")
#df_1

#unique(df_cleaned$MSZoning)

```


LotShape (Reg / IR1 / IR2 / IR3): General shape of property
We will categorise in order of rising irregularity as: 0, 1, 2, 3

LandContour (Low / Lvl / Bnk / HLS): Flatness of the property
We will categorise as 0, 1, 2, 3

LandSlope (Gtl / Mod / Sev): Slope of property
We will categorise as 0, 1, 2

```{r}
#df_2 = filter(df_cleaned, LandContour == "HLS" & LandSlope == "Gtl")
#df_2
```


Utilities (NoSewr / AllPub): Type of utilities available - Note that virtually all entries are AllPub (only 2 are 'NoSewr')
We will categorise as 0, 1 - but obviously it is not important to include this at all as there are not enough entries for training or prediction.

```{r}
#df_3 = filter(df_cleaned, Utilities == "NoSewr")
#df_3

df_3_1 = filter(df_cleaned, Electrical == "Mix")
df_3_1
# N.B. No entries in Electrical are categorised as 'Mix'
# So we categorise in rank order from poor to good as follows:
# FuseP, FuseF, FuseA, SBrkr
# 0, 1, 2, 3
```

LotConfig (Inside / Corner / CulDSac / FR2 / FR3): Lot configuration
We will categorise in order of desirability (4 being most desirable): 0, 1, 2, 3, 4

Neighborhood (): Physical locations within Ames city limits
One of the most significant categories. We will create a new neighborhood category, alongside original, that is an ordered int factor (based on EDA results):
Neighborhood_Int - 0, 1, 2, ..., 25, 26, 27
(MeadowV
BrDale
IDOTRR
BrkSide
OldTown
Edwards
SWISU
Landmrk
Sawyer
NPkVill
Blueste
NAmes
Mitchel
SawyerW
Gilbert
NWAmes
Greens
Blmngtn
CollgCr
Crawfor
ClearCr
Somerst
Timber
Veenker
GrnHill
StoneBr
NridgHt
NoRidge)

Condition1 (Norm / Feedr / Artery / RRAn / RRNn / RRAe / RRNe / PosA / PosN): Proximity to various conditions
Condition2 (Norm / Feedr / Artery / RRAn / RRNn / RRAe / RRNe / PosA / PosN): Proximity to various conditions (if more than one is present)
We will replace these two categories with three separate boolean categories:
IsOnMainroad - 0, 1     Is TRUE if either Condition1 or Condition 2 is Feedr or Artery
IsNearRailroad - 0, 1   Is TRUE if either Condition1 or Condition2 is RRAn, RRNn, RRAe, RRNe
IsNearPark - 0, 1       Is TRUE if either Condition1 or Condition2 is PosA, PosN


Feature Engineering for Land/Geography/Lot:

```{r}

#1 Delete LotFrontage

df_cleaned = select(df_cleaned, -LotFrontage)

#2 Construct RemodSinceBuilt and delete YearRemodAdd

df_cleaned$RemodSinceBuilt = as.integer(df_cleaned$YearRemodAdd - df_cleaned$YearBuilt)
df_cleaned = select(df_cleaned, -YearRemodAdd)

#3 Construct Age and delete YearBuilt

df_cleaned$Age = as.integer(year(df_cleaned$DateSold) - df_cleaned$YearBuilt)
df_cleaned = select(df_cleaned, -YearBuilt)

#4 Construct StreetAlley as ordered int factor and delete Street and Alley

df_cleaned$Street_temp = as.integer(0)
df_cleaned$Alley_temp = as.integer(0)

df_cleaned$Street_temp[df_cleaned$Street == "Grvl"] = as.integer(0)
df_cleaned$Street_temp[df_cleaned$Street == "Pave"] = as.integer(1)
df_cleaned$Alley_temp[df_cleaned$Alley == "NoAlley"] = as.integer(0)
df_cleaned$Alley_temp[df_cleaned$Alley == "Grvl"] = as.integer(1)
df_cleaned$Alley_temp[df_cleaned$Alley == "Pave"] = as.integer(2)

df_cleaned$StreetAlley = df_cleaned$Street_temp + df_cleaned$Alley_temp

df_cleaned$StreetAlley = as.factor(df_cleaned$StreetAlley)

df_cleaned$StreetAlley <- factor(df_cleaned$StreetAlley, levels = c(0, 1, 2, 3), ordered = TRUE)

df_cleaned = select(df_cleaned, -c(Street, Alley, Street_temp, Alley_temp))

#5 Convert LotShape into an ordered int factor

df_cleaned$LotShape_temp = as.integer(0)

df_cleaned$LotShape_temp[df_cleaned$LotShape == "Reg"] = as.integer(0)
df_cleaned$LotShape_temp[df_cleaned$LotShape == "IR1"] = as.integer(1)
df_cleaned$LotShape_temp[df_cleaned$LotShape == "IR2"] = as.integer(2)
df_cleaned$LotShape_temp[df_cleaned$LotShape == "IR3"] = as.integer(3)

df_cleaned$LotShape_temp = as.factor(df_cleaned$LotShape_temp)

df_cleaned$LotShape_temp = factor(df_cleaned$LotShape_temp, levels = c(0, 1, 2, 3), ordered = TRUE)

df_cleaned = select(df_cleaned, -LotShape)

df_cleaned = rename(df_cleaned, LotShape = LotShape_temp)

#6 Convert LandContour into an ordered int factor

df_cleaned$LandContour_temp = as.integer(0)

df_cleaned$LandContour_temp[df_cleaned$LandContour == "Low"] = as.integer(0)
df_cleaned$LandContour_temp[df_cleaned$LandContour == "Lvl"] = as.integer(1)
df_cleaned$LandContour_temp[df_cleaned$LandContour == "Bnk"] = as.integer(2)
df_cleaned$LandContour_temp[df_cleaned$LandContour == "HLS"] = as.integer(3)

df_cleaned$LandContour_temp = as.factor(df_cleaned$LandContour_temp)

df_cleaned$LandContour_temp = factor(df_cleaned$LandContour_temp, levels = c(0, 1, 2, 3), ordered = TRUE)

df_cleaned = select(df_cleaned, -LandContour)

df_cleaned = rename(df_cleaned, LandContour = LandContour_temp)

#7 Convert LandSlope into an ordered int factor

df_cleaned$LandSlope_temp = as.integer(0)

df_cleaned$LandSlope_temp[df_cleaned$LandSlope == "Gtl"] = as.integer(0)
df_cleaned$LandSlope_temp[df_cleaned$LandSlope == "Mod"] = as.integer(1)
df_cleaned$LandSlope_temp[df_cleaned$LandSlope == "Sev"] = as.integer(2)

df_cleaned$LandSlope_temp = as.factor(df_cleaned$LandSlope_temp)

df_cleaned$LandSlope_temp = factor(df_cleaned$LandSlope_temp, levels = c(0, 1, 2), ordered = TRUE)

df_cleaned = select(df_cleaned, -LandSlope)

df_cleaned = rename(df_cleaned, LandSlope = LandSlope_temp)

#8 Delete Utilities

df_cleaned = select(df_cleaned, -Utilities)

#9 Convert LotConfig into an ordered int factor

df_cleaned$LotConfig_temp = as.integer(0)

df_cleaned$LotConfig_temp[df_cleaned$LotConfig == "FR2"] = as.integer(0)
df_cleaned$LotConfig_temp[df_cleaned$LotConfig == "Inside"] = as.integer(1)
df_cleaned$LotConfig_temp[df_cleaned$LotConfig == "Corner"] = as.integer(2)
df_cleaned$LotConfig_temp[df_cleaned$LotConfig == "FR3"] = as.integer(3)
df_cleaned$LotConfig_temp[df_cleaned$LotConfig == "CulDSac"] = as.integer(4)

df_cleaned$LotConfig_temp = as.factor(df_cleaned$LotConfig_temp)

df_cleaned$LotConfig_temp = factor(df_cleaned$LotConfig_temp, levels = c(0, 1, 2, 3, 4), ordered = TRUE)

df_cleaned = select(df_cleaned, -LotConfig)

df_cleaned = rename(df_cleaned, LotConfig = LotConfig_temp)

#10 Creation of IsOnMainroad, IsNearRailroad, IsNearPark and deletion of Condition1 & 2

df_cleaned$IsOnMainroad = ifelse(df_cleaned$Condition1=="Feedr"|df_cleaned$Condition1=="Artery"|df_cleaned$Condition2=="Feedr"|df_cleaned$Condition2=="Artery", as.integer(1), as.integer(0))

df_cleaned$IsNearRailroad = ifelse(df_cleaned$Condition1=="RRAn"|df_cleaned$Condition1=="RRNn"|df_cleaned$Condition1=="RRAe"|df_cleaned$Condition1=="RRNe"|df_cleaned$Condition2=="RRAn"|df_cleaned$Condition2=="RRNn"|df_cleaned$Condition2=="RRAe"|df_cleaned$Condition2=="RRNe", as.integer(1), as.integer(0))

df_cleaned$IsNearPark = ifelse(df_cleaned$Condition1=="PosA"|df_cleaned$Condition1=="PosN"|df_cleaned$Condition2=="PosA"|df_cleaned$Condition2=="PosN", as.integer(1), as.integer(0))

df_cleaned$IsOnMainroad = as.factor(df_cleaned$IsOnMainroad)

df_cleaned$IsOnMainroad = factor(df_cleaned$IsOnMainroad, levels = c(0, 1), ordered = TRUE)

df_cleaned$IsNearRailroad = as.factor(df_cleaned$IsNearRailroad)

df_cleaned$IsNearRailroad = factor(df_cleaned$IsNearRailroad, levels = c(0, 1), ordered = TRUE)

df_cleaned$IsNearPark = as.factor(df_cleaned$IsNearPark)

df_cleaned$IsNearPark = factor(df_cleaned$IsNearPark, levels = c(0, 1), ordered = TRUE)

df_cleaned = select(df_cleaned, -c(Condition1,Condition2))

#11 Creation of Neighborhood_Int as ordered int factor

df_cleaned$Neighborhood_Int = as.integer(0)

df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "MeadowV"] = as.integer(0)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "BrDale"] = as.integer(1)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "IDOTRR"] = as.integer(2)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "BrkSide"] = as.integer(3)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "OldTown"] = as.integer(4)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Edwards"] = as.integer(5)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "SWISU"] = as.integer(6)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Landmrk"] = as.integer(7)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Sawyer"] = as.integer(8)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "NPkVill"] = as.integer(9)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Blueste"] = as.integer(10)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "NAmes"] = as.integer(11)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Mitchel"] = as.integer(12)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "SawyerW"] = as.integer(13)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Gilbert"] = as.integer(14)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "NWAmes"] = as.integer(15)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Greens"] = as.integer(16)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Blmngtn"] = as.integer(17)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "CollgCr"] = as.integer(18)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Crawfor"] = as.integer(19)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "ClearCr"] = as.integer(20)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Somerst"] = as.integer(21)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Timber"] = as.integer(22)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "Veenker"] = as.integer(23)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "GrnHill"] = as.integer(24)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "StoneBr"] = as.integer(25)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "NridgHt"] = as.integer(26)
df_cleaned$Neighborhood_Int[df_cleaned$Neighborhood == "NoRidge"] = as.integer(27)

df_cleaned$Neighborhood_Int = as.factor(df_cleaned$Neighborhood_Int)

df_cleaned$Neighborhood_Int = factor(df_cleaned$Neighborhood_Int, levels = c(0:27), ordered = TRUE)

#12 Convert CentralAir into an ordered int factor

df_cleaned$CentralAir_temp = as.integer(0)

df_cleaned$CentralAir_temp[df_cleaned$CentralAir == "N"] = as.integer(0)
df_cleaned$CentralAir_temp[df_cleaned$CentralAir == "Y"] = as.integer(1)

df_cleaned$CentralAir_temp = as.factor(df_cleaned$CentralAir_temp)

df_cleaned$CentralAir_temp = factor(df_cleaned$CentralAir_temp, levels = c(0, 1), ordered = TRUE)

df_cleaned = select(df_cleaned, -CentralAir)

df_cleaned = rename(df_cleaned, CentralAir = CentralAir_temp)

#13 Creation of MSZoning_Int as ordered int factor

df_cleaned$MSZoning_Int = as.integer(0)

df_cleaned$MSZoning_Int[df_cleaned$MSZoning == "A (agr)"] = as.integer(0)
df_cleaned$MSZoning_Int[df_cleaned$MSZoning == "C (all)"] = as.integer(1)
df_cleaned$MSZoning_Int[df_cleaned$MSZoning == "I (all)"] = as.integer(2)
df_cleaned$MSZoning_Int[df_cleaned$MSZoning == "RH"] = as.integer(3)
df_cleaned$MSZoning_Int[df_cleaned$MSZoning == "FV"] = as.integer(4)
df_cleaned$MSZoning_Int[df_cleaned$MSZoning == "RM"] = as.integer(5)
df_cleaned$MSZoning_Int[df_cleaned$MSZoning == "RL"] = as.integer(6)

df_cleaned$MSZoning_Int = as.factor(df_cleaned$MSZoning_Int)

df_cleaned$MSZoning_Int = factor(df_cleaned$MSZoning_Int, levels = c(0:6), ordered = TRUE)

# Relocate columns for tidyness

df_cleaned = df_cleaned %>%
  relocate(LotArea, .after = Rate) %>%
  relocate(Neighborhood, .after = GrLivArea) %>%
  relocate(IsNearPark, .after = Neighborhood) %>%
  relocate(IsNearRailroad, .after = Neighborhood) %>%
  relocate(IsOnMainroad, .after = Neighborhood) %>%
  relocate(LotConfig, .after = Neighborhood) %>%
  relocate(LandSlope, .after = Neighborhood) %>%  
  relocate(LandContour, .after = Neighborhood) %>%  
  relocate(LotShape, .after = Neighborhood) %>%  
  relocate(StreetAlley, .after = Neighborhood) %>%    
  relocate(RemodSinceBuilt, .after = Neighborhood) %>%   
  relocate(Age, .after = Neighborhood) %>%
  relocate(Neighborhood_Int, .after = Neighborhood) %>%
  relocate(CentralAir, .after = Neighborhood_Int) %>%
  relocate(MSZoning_Int, .after = Neighborhood_Int)
  
head(df_cleaned)

write.csv(df_cleaned, "df_cleaned.csv")

#df_4 = filter(df_cleaned, IsOnMainroad == "1")
#df_4

#levels(df_cleaned$StreetAlley)

```


This is a special script for Rishi's engineered csv. I want to replace the character date columns with the DateSold date column. Can't do it directly though his Python script, as his helpers script doesn't work in my Jupyter notebook.

What I will do is extract PID, DateSold, Rate from my df_cleaned dataframe and merge it with df_engineered.

Will also merge my other engineered features, and will make changes to the features everyone else has worked on that I think may improve model fitting.

```{r}

# Extract subset of columns from df_cleaned for insertion into df_engineered

df_temp = df_cleaned %>%
  select(PID, DateSold, Rate, logSalePrice, IsOnMainroad, IsNearPark, IsNearRailroad, LotConfig, LandSlope, LandContour, LotShape, StreetAlley, RemodSinceBuilt, Age, Neighborhood_Int, CentralAir, MSZoning_Int)

# Delete unnecessary columns from df_engineered

df_engineered = select(df_engineered, -c(X, YrSold, MoSold, LogSalePrice, LotFrontage, Street, Alley, LotShape, LandContour, Utilities, LotConfig, LandSlope, Condition1, Condition2, YearBuilt, YearRemodAdd, IsNearNegativeCondition, IsNearPositiveCondition, CentralAir))

# Merge df_temp with df_engineered

df_engineered = df_engineered %>%
  left_join(df_temp, by="PID") %>%
  relocate(DateSold, .after = PID) %>%
  relocate(SalePrice, .after = DateSold) %>%
  relocate(logSalePrice, .after = SalePrice) %>%
  relocate(Rate, .after = logSalePrice) %>%
  relocate(LotArea, .after = Rate) %>%
  relocate(Neighborhood, .after = GrLivArea) %>%
  relocate(IsNearPark, .after = Neighborhood) %>%
  relocate(IsNearRailroad, .after = Neighborhood) %>%
  relocate(IsOnMainroad, .after = Neighborhood) %>%
  relocate(LotConfig, .after = Neighborhood) %>%
  relocate(LandSlope, .after = Neighborhood) %>%  
  relocate(LandContour, .after = Neighborhood) %>%  
  relocate(LotShape, .after = Neighborhood) %>%  
  relocate(StreetAlley, .after = Neighborhood) %>%    
  relocate(RemodSinceBuilt, .after = Neighborhood) %>%   
  relocate(Age, .after = Neighborhood) %>%
  relocate(Neighborhood_Int, .after = Neighborhood) %>%
  relocate(CentralAir, .after = Neighborhood_Int) %>%
  relocate(MSZoning_Int, .after = Neighborhood_Int)
  
df_engineered =  df_engineered %>%
  arrange(ymd(df_engineered$DateSold), SalePrice)

head(df_engineered)

write.csv(df_engineered, "df_engineered.csv")

```


Correlation matrix:

```{r}

#df_eng_temp = df_engineered %>% 
#  mutate_if(is.character,as.factor)

model.matrix(~0+., data=df_engineered) %>% 
  cor(use="complete.obs") %>% 
  #cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag = F, type="lower", lab=FALSE, lab_size=0, tl.cex=0.5, tl.srt=90)

ggsave("fig1.pdf")


```


Exploratory Data Analysis:

```{r}

#1 LotArea

mean_1 = mean(df_cleaned$LotArea)
sd_1 = sd(df_cleaned$LotArea)

fig2 = ggscatter(df_cleaned, x = "LotArea", y = "SalePrice", 
          #add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          size = 0.15, color = "blue",
          cor.coef.coord = c(7.5e4,5e5),
          xtickslab.rt = 45,
          xlab = "Lot Area (sq feet)", ylab = "SalePrice (USD)") +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold"))  + annotate(geom = "text", label = paste("Mean = ", signif(mean_1,4), "\nStandard Dev = ", signif(sd_1,4)),
           x = 7.4e4,
           y = 6e5,
           angle = 0,
           hjust=0,
           #colour = "blue",
           fontface =2)

fig3 = ggscatter(df_cleaned, x = "LotArea", y = "logSalePrice", 
          add = "reg.line", conf.int = TRUE, 
          #cor.coef = TRUE, cor.method = "pearson",
          size = 0.15, color = "blue",
          cor.coef.coord = c(1.25e4,6),
          xtickslab.rt = 45,
          xlab = "Lot Area (sq feet)", ylab = "log(SalePrice)",
          xlim = c(0,30000), ylim=c(4,6.25)) +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold"))# + annotate(geom = "text", label = paste("Mean = ", signif(mean_1,2), "\nStandard Dev = ", signif(sd_1,2)),
#           x = 2.4,
#           y = 5e5,
#           angle = 0,
#           hjust=0,
#           #colour = "blue",
#           fontface =2)

fig2 + fig3

ggsave("fig2-3.pdf")


#2 Neighbourhood

cor.result_2 = cor.test(as.integer(df_cleaned$Neighborhood_Int), df_cleaned$SalePrice, method=c("pearson"))

fig4 = ggplot(df_cleaned, aes(x = reorder(Neighborhood, SalePrice), y = SalePrice, fill=Neighborhood)) +
        geom_boxplot(outlier.size = 0.5) +
        labs(x="Neighborhood") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=1, color="red", fill="black")         + theme(legend.position = "none") + theme(axis.text = element_text(face="bold")) + theme(axis.title = element_text(face="bold"))  + annotate(geom = "text", label = paste("R = ", signif(cor.result_2$estimate,2)),
           x = 4,
           y = 5.5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig4

ggsave("fig4.pdf")

#3 RemodSinceBuilt

mean_3 = mean(df_cleaned$RemodSinceBuilt)
sd_3 = sd(df_cleaned$RemodSinceBuilt)

fig5 = ggscatter(df_cleaned, x = "RemodSinceBuilt", y = "logSalePrice", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          size = 0.25, color = "blue",
          cor.coef.coord = c(0,4.25),
          xtickslab.rt = 45,
          xlab = "Period Between Remodel and Build Date (years)", ylab = "SalePrice (USD)")         + theme(axis.text = element_text(face="bold")) +
          theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("Mean = ", signif(mean_3,4), "\nStandard Dev = ", signif(sd_3,4)),
           x = 80,
           y = 4.33,
           angle = 0,
           hjust=0,
           #colour = "blue",
           fontface =2)

fig5

ggsave("fig5.pdf")

#4 Age

mean_4 = mean(df_cleaned$Age)
sd_4 = sd(df_cleaned$Age)

fig6 = ggscatter(df_cleaned, x = "Age", y = "logSalePrice", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          size = 0.25, color = "blue",
          cor.coef.coord = c(0,4.25),
          xtickslab.rt = 45,
          xlab = "Age (years)", ylab = "SalePrice (USD)")  +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("Mean = ", signif(mean_4,4), "\nStandard Dev = ", signif(sd_4,4)),
           x = 80,
           y = 4.33,
           angle = 0,
           hjust=0,
           #colour = "blue",
           fontface =2)

fig6

ggsave("fig6.pdf")

#5 StreetAlley

cor.result_5 = cor.test(as.integer(df_cleaned$StreetAlley), df_cleaned$SalePrice, method=c("pearson"))

fig7 = ggplot(df_cleaned, aes(x = reorder(StreetAlley, SalePrice), y = SalePrice, fill=StreetAlley)) +
        geom_boxplot() +
        labs(x="StreetAlley") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black") + theme(legend.position = c(0.75,0.4)) + scale_fill_discrete(labels = c("Gravel / NoAlley (0)", "Paved / NoAlley (1)", "Paved / Gravel (2)", "Paved / Paved (3)"))  +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_6$estimate,2), "\np-value = ", signif(cor.result_6$p.value,2)),
           x = 0.9,
           y = 4.1e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig7

ggsave("fig7.pdf")

#6 LotShape

cor.result_6 = cor.test(as.integer(df_cleaned$LotShape), df_cleaned$SalePrice, method=c("pearson"))

fig8 = ggplot(df_cleaned, aes(x = reorder(LotShape, SalePrice), y = SalePrice, fill=LotShape)) +
        geom_boxplot() +
        labs(x="Lot Shape") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black") + theme(legend.position = c(0.87,0.62)) + scale_fill_discrete(labels = c("Regular (0)", "Irregular1 (1)", "Irregular2 (2)", "Irregular3 (3)")) +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_6$estimate,2), "\np-value = ", signif(cor.result_6$p.value,2)),
           x = 1.5,
           y = 5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig8

ggsave("fig8.pdf")

#7 LandContour

cor.result_7 = cor.test(as.integer(df_cleaned$LandContour), df_cleaned$SalePrice, method=c("pearson"))

fig9 = ggplot(df_cleaned, aes(x = reorder(LandContour, SalePrice), y = SalePrice, fill=LandContour)) +
        geom_boxplot() +
        labs(x="Land Contour") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black") + theme(legend.position = c(0.87,0.62)) + scale_fill_discrete(labels = c("Low (0)", "Level (1)", "Banked (2)", "Hillside (3)")) +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_7$estimate,2), "\np-value = ", signif(cor.result_7$p.value,2)),
           x = 1.5,
           y = 5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig9

ggsave("fig9.pdf")

#8 LandSlope

cor.result_8 = cor.test(as.integer(df_cleaned$LandSlope), df_cleaned$SalePrice, method=c("pearson"))

fig10 = ggplot(df_cleaned, aes(x = reorder(LandSlope, SalePrice), y = SalePrice, fill=LandSlope)) +
        geom_boxplot() +
        labs(x="Land Slope") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black")       + theme(legend.position = c(0.842,0.75)) + scale_fill_discrete(labels = c("Gentle (0)", "Moderate (1)", "Severe (2)")) + theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_8$estimate,2), "\np-value = ", signif(cor.result_8$p.value,2)),
           x = 1.5,
           y = 5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig10

ggsave("fig10.pdf")

#9 LotConfig

cor.result_9 = cor.test(as.integer(df_cleaned$LotConfig), df_cleaned$SalePrice, method=c("pearson"))

fig11 = ggplot(df_cleaned, aes(x = reorder(LotConfig, SalePrice), y = SalePrice, fill=LotConfig)) +
        geom_boxplot() +
        labs(x="Lot Configuration") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black") + theme(legend.position = c(0.87,0.6)) + scale_fill_discrete(labels = c("2-Side Frontage (0)", "Inside Lot (1)", "Corner Lot (2)", "3-Side Frontage (3)", "Cul De Sac (4)")) +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_9$estimate,2), "\np-value = ", signif(cor.result_9$p.value,2)),
           x = 1.4,
           y = 5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig11

ggsave("fig11.pdf")

#10 IsOnMainroad

cor.result_10 = cor.test(as.integer(df_cleaned$IsOnMainroad), df_cleaned$SalePrice, method=c("pearson"))

fig12 = ggplot(df_cleaned, aes(x = reorder(IsOnMainroad, SalePrice), y = SalePrice, fill=IsOnMainroad)) +
        geom_boxplot() +
        labs(x="Is On Mainroad?") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black")       + theme(legend.position = c(0.842,0.5)) + scale_fill_discrete(labels = c("No (0)", "Yes (1)")) + theme(axis.text = element_text(face="bold")) + theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_10$estimate,2), "\np-value = ", signif(cor.result_10$p.value,2)),
           x = 2.4,
           y = 5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig12

ggsave("fig12.pdf")

#11 IsNearRailroad

cor.result_11 = cor.test(as.integer(df_cleaned$IsNearRailroad), df_cleaned$SalePrice, method=c("pearson"))

fig13 = ggplot(df_cleaned, aes(x = reorder(IsNearRailroad, SalePrice), y = SalePrice, fill=IsNearRailroad)) +
        geom_boxplot() +
        labs(x="Is Near Railroad?") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black")       + theme(legend.position = c(0.842,0.5)) + scale_fill_discrete(labels = c("No (0)", "Yes (1)")) + theme(axis.text = element_text(face="bold")) + theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_11$estimate,2), "\np-value = ", signif(cor.result_11$p.value,2)),
           x = 2.4,
           y = 5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig13

ggsave("fig13.pdf")

#12 IsNearPark

cor.result_12 = cor.test(as.integer(df_cleaned$IsNearPark), df_cleaned$SalePrice, method=c("pearson"))

fig14 = ggplot(df_cleaned, aes(x = reorder(IsNearPark, SalePrice), y = SalePrice, fill=IsNearPark)) +
        geom_boxplot() +
        labs(x="Is Near Park?") +
        coord_flip() +
        stat_summary(fun.y=mean, geom="point", shape=17, size=2, color="red", fill="black")       + theme(legend.position = c(0.842,0.5)) + scale_fill_discrete(labels = c("No (0)", "Yes (1)")) + theme(axis.text = element_text(face="bold")) + theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("R = ", signif(cor.result_12$estimate,2), "\np-value = ", signif(cor.result_12$p.value,2)),
           x = 2.4,
           y = 5e5,
           angle = 0,
           hjust=0,
           colour = "blue",
           fontface =2)
        
fig14

ggsave("fig14.pdf")

#13 Rate

mean_13 = mean(df_cleaned$Rate)
sd_13 = sd(df_cleaned$Rate)

fig15 = ggscatter(df_cleaned, x = "Rate", y = "SalePrice", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          size = 0.25, color = "blue",
          #cor.coef.coord = c(0,0),
          xtickslab.rt = 45,
          xlab = "Interest Rate (%)", ylab = "SalePrice (USD)") +
        theme(axis.text = element_text(face="bold")) +
        theme(axis.title = element_text(face="bold")) + annotate(geom = "text", label = paste("Mean = ", signif(mean_13,2), "\nStandard Dev = ", signif(sd_13,2)),
           x = 2.4,
           y = 5e5,
           angle = 0,
           hjust=0,
           #colour = "blue",
           fontface =2)

fig15

ggsave("fig15.pdf")

#13 Time Series





```



