---
title: "Akram_Dataframe_Engineering"
output: html_document
---

Load packages:

```{r}
library(Quandl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(tidyquant)
library(patchwork)
library(lubridate)
library(zoo)

path = "~/Desktop/NYCDSA/Homework/Project3/Akram/EDA"
setwd(path)

```

Import data frames:

```{r}

df_cleaned = read.csv("~/Desktop/NYCDSA/Homework/Project3/Akram/Data/cleaned.csv")

df_engineered = read.csv("~/Desktop/NYCDSA/Homework/Project3/Akram/Data/engineered.csv")

Ames_Start = as.Date("2006-01-01")
Ames_End = as.Date("2010-12-31")


TNX = tq_get("^TNX",
             from = Ames_Start,
             to = Ames_End,
             get = "stock.prices"
             ) %>%
  select(date, adjusted) %>%
  rename(rate = adjusted)

TNX = TNX %>%
  group_by(DateSold = lubridate::floor_date(date, "month")) %>%
  summarise(Rate = mean(rate, na.rm=TRUE))

head(TNX)

df_cleaned = df_cleaned %>% 
  mutate(
    DaySold = as.integer(1), 
    DateSold = make_date(YrSold,MoSold,DaySold)
  )

df_cleaned = df_cleaned %>%
  relocate(DateSold, .after = PID) %>%
  relocate(SalePrice, .before = GrLivArea) %>%
  select(-c(X, YrSold, MoSold, DaySold)) %>%
  arrange(ymd(df_cleaned$DateSold), SalePrice)

head(df_cleaned)

```

Merge interest rate with main dataframe:

```{r}

# First, create logSalePrice column

df_cleaned$logSalePrice = log10(df_cleaned$SalePrice)

# Merge TNX with df_cleaned

df_cleaned = df_cleaned %>%
  left_join(TNX, by="DateSold") %>%
  relocate(Rate, .after = SalePrice) %>%
  relocate(logSalePrice, .after = SalePrice)

head(df_cleaned)


```


This is a special script for Rishi's engineered csv. I want to replace the character date columns with the DateSold date column. Can't do it directly though his Python script, as helpers isn't working in my Jupyter notebook.

What I will do is extract PID, DateSold, Rate from my df_cleaned dataframe and merge it with df_engineered.

N.B. Might have to move this part to after I do my own feature engineering on df_cleaned.

```{r}

# Extract subset of columns from df_cleaned for insertion into df_engineered

df_temp = df_cleaned %>%
  select(PID, DateSold, Rate, logSalePrice)

# Merge df_temp with df_engineered

df_engineered = df_engineered %>%
  left_join(df_temp, by="PID") %>%
  relocate(DateSold, .after = PID) %>%
  relocate(SalePrice, .after = DateSold) %>%
  relocate(logSalePrice, .after = SalePrice) %>%
  relocate(Rate, .after = logSalePrice) %>%
  select(-c(X, YrSold, MoSold, LogSalePrice))

df_engineered =  df_engineered %>%
  arrange(ymd(df_engineered$DateSold), SalePrice)

head(df_engineered)

```


