---
title: "Preprocess / Clean Housing Data"
author: "Rishi Goutam"
date: "2/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Read housing data

```{r echo=FALSE, message=FALSE}
housing = readr::read_csv("../data/Ames_Housing_Price_Data.csv")
sapply(housing, class)
```


```{r echo=TRUE, message=FALSE}
# first column is empty string ``, renamed to `...1` by readr
colnames(housing)
nrow(housing)
ncol(housing)
head(housing)
```

Basic Statistics

``` {r summary}
summary(housing)
```


Frequency Distribution

```{r feature-groups}

# GUID: PID
# Target variable: SalePrice

categorical.cols <- c("MSSubClass", "MSZoning", "Street", "Alley", "LotShape", "LandContour", "Utilities", "LotConfig", "LandSlope", "Neighborhood", "Condition1", "Condition2", "BldgType", "HouseStyle", "OverallQual", "OverallCond", "RoofStyle", "RoofMatl", "Exterior1st", "Exterior2nd", "MasVnrType", "ExterQual", "ExterCond", "Foundation", "BsmtQual", "BsmtCond", "BsmtExposure", "BsmtFinType1", "BsmtFinType2", "Heating", "HeatingQC", "CentralAir", "Electrical", "KitchenQual", "TotRmsAbvGrd", "Functional", "Fireplaces", "FireplaceQu", "GarageType", "GarageFinish", "GarageCars", "GarageQual", "GarageCond", "PavedDrive", "PoolQC", "Fence", "MiscFeature", "SaleType", "SaleCondition", "MoSold", "YrSold")

numerical.cols <- c("GrLivArea", "LotFrontage", "LotArea", "YearBuilt", "YearRemodAdd", "MasVnrArea", "BsmtFinSF1", "BsmtFinSF2", "BsmtUnfSF", "TotalBsmtSF", "1stFlrSF", "2ndFlrSF", "LowQualFinSF", "GarageYrBlt", "GarageArea", "WoodDeckSF", "OpenPorchSF", "EnclosedPorch", "3SsnPorch", "ScreenPorch", "PoolArea", "MiscVal")

boolean.cols <- c("BsmtFullBath", "BsmtHalfBath", "FullBath", "HalfBath", "BedroomAbvGr", "KitchenAbvGr")

# dates <- c("YearBuilt", "YearRemodAdd", "GarageYrBlt", "MoSold", "YrSold")

# Cast housing df columns to correct type
housing[categorical.cols] <- sapply(housing[categorical.cols], forcats::as_factor)
housing[numerical.cols] <- sapply(housing[numerical.cols], as.numeric)
housing[boolean.cols] <- sapply(housing[boolean.cols], as.logical)

```


```{r histograms, echo=FALSE}
library(Hmisc)

# Histograms of the numeric values
hist.data.frame(housing[numerical.cols], freq = TRUE, na.big = TRUE, rugs = FALSE)
# n: number of values, m: number of missing values
```

From above, 
* LotFrontage missing 462
* MasVnrArea missing 14
* BsmtFinSF1 missing 1
* BsmtFinSF2 missing 1
* TotalBsmtSF missing 1
* GarageYrBlt missing 129
* GarageArea missing 1

Can we impute values in any logical manner? Can we safely drop non-imputable values?

What about non-numeric values?

TODO impute missing values

```{r impute-missing-values}
# TODO
```

TODO remove NAs

```{r remove-NAs}

```


```{r scatterplots, echo=FALSE}
# Scatterplots of the numerical columsn vs target

# https://stackoverflow.com/questions/24648729/plot-one-numeric-variable-against-n-numeric-variables-in-n-plots
library(reshape2)

numerics_plus_SalePrice <- housing %>%
  select(c("SalePrice", numerical.cols))
housing.numerics.vs.SalePrice <- melt(numerics_plus_SalePrice, "SalePrice")

housing.numerics.vs.SalePrice %>%
  ggplot(aes(value, SalePrice)) +
  geom_point() +
  facet_wrap(~variable, scales = "free")
```

From above, we see a linear relationship between SalePrice and the following:
* Area. Bigger houses sell for more
* Year built/remodeled. Newer houses are more expensive (though some interesting increase for <1900)


We can plot the SalePrice. We see that there are lots of outliers and the SalePrice is right-skewed
```{r SalePrice-distribution}
housing %>% 
  ggplot(aes(x = SalePrice)) +
  geom_histogram(binwidth = 5000)

housing %>% 
  ggplot(aes(x = SalePrice)) +
  geom_density()

housing %>% 
  ggplot(aes(x = SalePrice)) +
  geom_boxplot()
```
By taking the natural log of SalePrice, we can get a more normal distribution, though now left-skewed
```{r log-SalePrice}
housing %>% 
  ggplot(aes(x = log(SalePrice))) +
  geom_histogram()

housing %>% 
  ggplot(aes(x = log(SalePrice))) +
  geom_density()
```

TODO Handling outliers

Do we remove them? Look at SaleCond for Abnormal sales
```{r outliers}

```

TODO Check for multicolinearity by looking at R^2 matrix. Need to remove NAs I think
```{r correlation-matrix}
# See: https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html
library(corrplot)
housing.cors <- cor(housing[numerical.cols])
corrplot(housing.cors)
```

